Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
wording: set expectations -> express expectations

\item
    Introduce a set of combinators to set expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

@@

We propose several combinators, that can be used to set expectations
about the outcome of examples.  And we build them on top of
HUnit.

@@

>>>>

\item
    Introduce a set of combinators to express expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

@@

We propose several combinators which can be used to express expectations
about the outcome of examples.  These are built on top of HUnit.

@@

\subsection{TBD}

\begin{itemize}
    \item \emph{optional}: Bridging the gap between HUnit and QuickCheck
    \item
        Feedback for failing QuickCheck properties is not always as
        useful as it could be -> combinators that use QuickCheck's
        Result type could help
    \item
        Are more high-lever approaches to BDD, akin to Ruby's
        Cucumber, applicable to Haskell? (Observation: Cucumber's
        approach is tightly tied to OO)
\end{itemize}
